\documentclass[9pt, letterpad]{extarticle}

\usepackage{fontspec}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage[none]{hyphenat}
\usepackage[colorlinks=true,
			linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{xcolor}
\usepackage{emoji}
\usepackage{fontawesome}
\usepackage[subtle]{savetrees}
\geometry{
	letterpaper,
	left=0.60cm,
	right=0.60cm,
	top=0.60cm,
	bottom=0.60cm
}

\setmainfont{Lato}
\titleformat{\section}
{\large\vspace*{-0.25em}}{}{0em}{\textbf}[\titlerule]
\titlespacing*{\section}{0pt}{0.5em}{0.5em}

\titleformat{\subsection}[runin]
{\large\vspace*{-0.25em}}{}{0.25em}{\textbf}
\titlespacing*{\subsection}{0pt}{0.5em}{0.5em}

\renewcommand{\maketitle}[6]{
	\begin{center}
	\Large{\bfseries\scshape{#1}} \\
	\vspace*{0.25em}
	\small {#2} \\
	\vspace*{0.25em}
	\faPhoneSquare \hspace{0.1em} {#3} \hspace*{0.5em}
	\faEnvelope \hspace{0.1em} \href{mailto:#4}{#4} \hspace*{0.5em}
	\faLinkedinSquare \hspace{0.1em} \href{https://#5}{#5} \hspace{0.5em}
	\faGithubSquare \hspace{0.1em} \href{https://#6}{#6}
	\end{center}
}

\newcommand{\cmpnysection}[4] {
	\raggedright{\large\bfseries{#1}}
	\hfill {\small #2} \\
	{#3}
	\hfill {\small #4} \\
}

\newcommand{\projsection}[2] {
	\raggedright{\normalsize\bfseries{#1}} | {\small \textit{Source Code:} \hspace{0.1em} \href{#2}{#2}}
}
\titlespacing*{\projsection}{0pt}{0.5em}{0.5em}

\newcommand{\edusection}[5] {
	\normalsize{\textbf{#1} | {#3} | {#4}
	\hfill {\small #2} } \\
	{\small #5} }

\begin{document}
\maketitle
{Vinodh Balakrishna}
{Software Engineer | C/C++ Programmer | GNU/Linux Enthusiast}
{(913) 326 4029}
{vinodh.b.27@gmail.com}
{www.linkedin.com/in/vinodh27}
{www.github.com/v1n0dh}

\thispagestyle{empty}

\noindent
\section{Professional Summary}
Software Engineer with around 2 years of experience in developing efficient and secure Linux firmware for embedded systems. Skilled in C/C++, Python, Rust, and shell scripting, with deep expertise in GNU/Linux environments. Specializes in system performance optimization, low-level programming, and implementing robust security solutions.

\section{Technical Skills}
\textbf{Programming Languages:} C/C++, Python, Shell Scripting, Java, Rust, Assembly (Basic) \\
\textbf{Operating Systems:} GNU Linux/Unix Systems, Embedded Linux Firmware \\
\textbf{Networking:} TCP/IP, UDP, SNMP, Networking Protocols \\
\textbf{Tools and Technologies:} Yocto Project, RDK, Data Structures, CMake, GDB, QEMU, OpenSSL, Wireshark, Jenkins, Git, Splunk, Vim

\section{Experience}
\cmpnysection
{Comcast}
{Chennai, India}
{{\bfseries Embedded Linux Engineer} | Platform Security Team (TPX)}
{Dec 2021 - July 2023}
\vspace*{-0.5em}
\begin{itemize}[leftmargin=6mm]
	\setlength\itemsep{0em}
	\item{Utilized the Yocto Project build system to design, develop, and maintain custom Linux firmware based on the RDK software stack for over 1 million CPE devices, including set-top boxes, routers, and TVs.}
	\item{Enhanced security in the custom WalledGarden Shell by implementing command logging and blocking unauthorized commands, significantly improving secure SSH access to CPE devices.}
	\item{Implemented a Tab Completion feature in the WalledGarden Shell using the readline library and a multi-threaded approach, enhancing user experience and increasing shell efficiency by 40\%}
	\item{Integrated Software Bill of Materials (SBOM) functionality into the build system by meticulously tracking all software components, enhancing supply chain security and ensuring 100\% transparency in the final product's software inventory.}
	\item{Enabled firmware security feature Address Space Layout Randomization (ASLR) for multiple RDKB devices by implementing position-independent code, which significantly reduced memory-related security vulnerabilities.}
	\item{Maintained and renewed XPKI certificates for TLS communications within various internal components, enhancing data protection and ensuring reliable, encrypted interactions between system components.}
	\item{Securely removed the video analytics module from RDKB devices, optimizing firmware performance, improving system efficiency, and reducing maintenance overhead.}
\end{itemize}

\cmpnysection
{Cognizant}
{Bangalore, India}
{\bfseries Programmer Analyst Trainee (Intern)}
{Aug 2021 - Dec 2021}
\vspace*{-0.5em}
\begin{itemize}[leftmargin=6mm]
	\setlength\itemsep{0em}
	\item{Led a Proof of Concept to integrate ShellCheck for automated shell script error detection, improving the development and code review process.}
\end{itemize}


\section{Education}
\edusection
{University of Central Missouri}
{Aug 2023 {-} Present}
{Masters {-} Computer Science}
{\textit{Grade:} 3.12 / 4.00 (CGPA)}
{Coursework: Operating Systems, Algorithms, Computer Networking \& Security, Compiler Design \& Construction, Design of Cryptographic Algorithms, Web Application Security, Cloud Security}
\vspace*{0.5em}

\edusection
{Bharath Institute of Higher Education and Research}
{2017 {-} 2021}
{B.Tech {-} Computer Science Engineering}
{\textit{Grade:} 8.4 / 10.0}
{}

\section{Projects}
\projsection
{Vshell}
{https://github.com/v1n0dh/vshell}
\vspace*{-0.5em}
\begin{itemize}[leftmargin=6mm]
	\setlength\itemsep{0em}
	\item{Developed a custom shell in C++, inspired by a coding challenge at \href{https://codingchallenges.fyi/challenges/challenge-shell}{\underline {codingchallenges.fyi}}, closely resembling bash.}
	\item{Incorporated key shell features, including command execution, I/O redirection, and pipes, facilitating efficient user interaction with the system.}
	\item{Integrated tab completion for files and command history, enhancing user experience and productivity.}
	\item{Successfully used by developers in testing environments, showcasing effectiveness in managing command-line tasks.}
\end{itemize}

\projsection
{System Metrics Display for dwm}
{https://github.com/v1n0dh/dwmstatus}
\vspace*{-0.5em}
\begin{itemize}[leftmargin=6mm]
	\setlength\itemsep{0em}
	\item{Created a custom status bar for the dwm window manager using C programming, displaying real-time system metrics such as network speeds, Wi-Fi network, CPU temperature, RAM usage, battery status, and clock.}
	\item{Gathered system statistics directly from low-level file structures like \textit{/sys/class} for battery and network information, and used X11 library to dynamically update the status bar.}
	\item{Integrated network speed calculation by monitoring changes in RX/TX bytes and implemented Wi-Fi network detection using shell commands.}
	\item{Optimized system resource usage by writing efficient C code, providing critical information without relying on external tools or scripts.}
\end{itemize}

\projsection
{Bencode Parser}
{https://github.com/v1n0dh/Bencode-Parser}
\vspace*{-0.5em}
\begin{itemize}[leftmargin=6mm]
	\setlength\itemsep{0em}
	\item{Developed a parser that converts Bencoded data (used in torrent files) into a human-readable JSON format.}
	\item{Built in C++ utilizing the Jsoncpp library for JSON object handling, creating an API making it handy for handling Bencoded data, enhancing compatibility.}
\end{itemize}

\section{Certifications}
\begin{itemize}[leftmargin=6mm]
	\setlength\itemsep{0em}
	\item{Rust Essential Training by Barron Stone, Linkedin Learnings} | \href{https://www.linkedin.com/learning/certificates/5b0eb9a5191ed3a4cb605f7b8b9e5864ed123e5b13b5f8f68bfc99b6ff8cd87d?trk=share_certificate}{\underline {Certificate Link} \faExternalLink}
	\item{Linux Device Drivers by Kevin Dankwardt, Linkedin Learnings} | \href{https://www.linkedin.com/learning/certificates/ef2284b25b44e40cdb305a085b6a77f7a4f0eac3762a844f5530279dd01a9549?trk=share_certificate}{\underline {Certificate Link} \faExternalLink}
\end{itemize}

\end{document}
